---
title: "lab9A"
author: "Kate Newcomer"
date: "November 8, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(stringr)
library(tidyverse)
```
14.3.1 Basic Matches
```{r eval=FALSE}
x <- c("apple", "banana", "pear")
str_view(x, "an")
str_view(x, ".a.")

```

```{r eval=FALSE}
# To create the regular expression, we need \\
dot <- "\\."

# But the expression itself only contains one:
writeLines(dot)
```
```{r eval=FALSE}
# And this tells R to look for an explicit .
x <- c("abc", "a.c", "bef")
str_view(x, "a\\.c")

x <- "a\\b"
writeLines(x)

str_view(x, "\\\\")
```
###  14.3.1.1 Exercises
1.  Explain why each of these strings don’t match a \: "\", "\\", "\\\".
A.  Each string represents a different value. For example "\" will cause the escape of the next character in the R string. "\\" will simplify to \ in the regex, which will cause the escape of the next character in the string. "\\\" will simplify to "\\" given that the first two slashes will resolve to a backslash followed by the last backlash. This will cause the release of some escaped character

2. How would you match the sequence "'\ ?
```{r}
 str_view("\"'\\", "\"'\\\\", match = TRUE)
```
3. What patterns will the regular expression \..\..\.. match? How would you represent it as a string?
A. Any patterns that are a dot followed by a character repeated three times
```{r}

str_view(c(".a.b.c", ".a.b", "....."), c("\\..\\..\\.."), match = TRUE)
```

1.4.3.2 Anchors
```{r eval=FALSE}
x <- c("apple", "banana", "pear")
str_view(x, "^a")

str_view(x, "a$")

x <- c("apple pie", "apple", "apple cake")
str_view(x, "apple")

str_view(x, "^apple$")

```
### 14.3.2.1 Exercises
1. How would you match the literal string "$^$"?
```{r}
str_view(c("$^$", "ab$^$sfas"), "^\\$\\^\\$$", match = TRUE)
```
2. Given the corpus of common words in stringr::words, create regular expressions that find all words that:
Start with “y”.
```{r}
 str_view(c("$^$", "ab$^$sfas"), "^\\$\\^\\$$", match = TRUE)
```
End with "x"
```{r}
str_view(c("$^$", "ab$^$sfas"), "^\\$\\^\\$$", match = TRUE)

```
 Are exactly three letters long. (Don’t cheat by using str_length()!)
```{r}
str_view(stringr::words, "^...$", match = TRUE)
```
 Have seven letters or more.
```{r}

str_view(stringr::words, "^...$", match = TRUE)
```

##1.4.4.1

```{r eval=FALSE}
x <- c("apple", "banana", "pear")
str_detect(x, "e") 

# How many common words start with t?
sum(str_detect(words, "^t"))

# What proportion of common words end with a vowel?
mean(str_detect(words, "[aeiou]$"))

# Find all words containing at least one vowel, and negate
no_vowels_1 <- !str_detect(words, "[aeiou]")

# Find all words consisting only of consonants (non-vowels)
no_vowels_2 <- str_detect(words, "^[^aeiou]+$")
identical(no_vowels_1, no_vowels_2)

words[str_detect(words, "x$")]

str_subset(words, "x$")

df <- tibble(
  word = words, 
  i = seq_along(word)
)
df %>% 
  filter(str_detect(word, "x$"))

x <- c("apple", "banana", "pear")
str_count(x, "a")

df %>% 
  mutate(
    vowels = str_count(word, "[aeiou]"),
    consonants = str_count(word, "[^aeiou]")
  )

```
###14.4.1.1 Exercises
1. For each of the following challenges, try solving it by using both a single regular expression, and a combination of multiple str_detect() calls.

2. Find all words that start or end with x.
words[str_detect(words, "^x|x$")]
```{r}
start_with_x <- str_detect(words, "^x")
end_with_x <- str_detect(words, "x$")
words[start_with_x | end_with_x]
```

3. Find all words that start with a vowel and end with a consonant.

```{r}
start_with_x <- str_detect(words, "^x")
end_with_x <- str_detect(words, "x$")
words[start_with_x | end_with_x]
```
4. Are there any words that contain at least one of each different vowel?
```{r}
start_with_x <- str_detect(words, "^x")
end_with_x <- str_detect(words, "x$")
words[start_with_x | end_with_x]

```

5. What word has the highest number of vowels? What word has the highest proportion of vowels? (Hint: what is the denominator?)

```{r}
start_with_x <- str_detect(words, "^x")
end_with_x <- str_detect(words, "x$")
words[start_with_x | end_with_x]

```
###14.4.2.1 Exercises
1. In the previous example, you might have noticed that the regular expression matched “flickered”, which is not a colour. Modify the regex to fix the problem.
```{r}
colours <- c("red", "orange", "yellow", "green", "blue", "purple") %>% 
  paste0(" ", .)

colour_match <- str_c(colours, collapse = "|")

more <- sentences[str_count(sentences, colour_match) > 1]
str_view_all(more, colour_match)
```

2. From the Harvard sentences data, extract:
The first word from each sentence.
```{r}
str_extract(sentences, "[A-Za-z][A-Za-z']*") %>% head()
```
All words ending in ing.
```{r}
pattern <- "\\b[A-Za-z]+ing\\b"
sentences_with_ing <- str_detect(sentences, pattern)
unique(unlist(str_extract_all(sentences[sentences_with_ing], pattern))) %>%
  head()


```

All plurals.
```{r}
unique(unlist(str_extract_all(sentences, "\\b[A-Za-z]{3,}s\\b"))) %>%
  head()
```

###14.4.3.1 Exercises
1.   Find all words that come after a “number” like “one”, )
```{r}
#Create regex expression
nums <- c("one", "two", "three", "four", "five", "six", "seven", "eight", "nine")

nums_c <- str_c(nums, collapse = "|")

# see stringr cheatsheet: "(?<![:alpha:])" means not preceded by
re <- str_c("(", "(?<![:alpha:])", "(", nums_c, "))", " ", "([^ \\.]+)", 
            sep = "")

sentences %>% 
  str_subset(regex(re, ignore_case = TRUE)) %>% 
  str_extract_all(regex(re, ignore_case = TRUE)) %>% 
  unlist() %>% 
  tibble::enframe(name = NULL) %>% 
  separate(col = "value", 
           into = c("num", "following"),
           remove = FALSE)



```
2. Find all contractions. Separate out the pieces before and after the apostrophe.
```{r}
#note the () facilitate the split with functions
contr <- "([^ \\.]+)'([^ \\.]*)"
sentences %>% 
  #note the improvement this word definition is to the above [^ ]+ 
  str_subset(contr) %>% 
  str_match_all(contr)
```

14.4.4.1
1. Replace all forward slashes in a string with backslashes.
```{r}
str_replace_all("past/present/future", "/", "\\\\")
```

2. Implement a simple version of str_to_lower() using replace_all().
```{r}
replacements <- c("A" = "a", "B" = "b", "C" = "c", "D" = "d", "E" = "e",
                  "F" = "f", "G" = "g", "H" = "h", "I" = "i", "J" = "j", 
                  "K" = "k", "L" = "l", "M" = "m", "N" = "n", "O" = "o", 
                  "P" = "p", "Q" = "q", "R" = "r", "S" = "s", "T" = "t", 
                  "U" = "u", "V" = "v", "W" = "w", "X" = "x", "Y" = "y", 
                  "Z" = "z")
lower_words <- str_replace_all(words, pattern = replacements)
head(lower_words)
```
3. Switch the first and last letters in words. Which of those strings are still words?

```{r}
swapped <- str_replace_all(words, "^([A-Za-z])(.*)([A-Za-z])$", "\\3\\2\\1")
intersect(swapped, words)
```

14.4.5.1 Exercises

1. Split up a string like “apples, pears, and bananas” into individual components.
```{r}
x <- "apples, pears, and bananas"
str_split(x, ",* ")  #note that regular expression works to handle commas as well
```

2. Why is it better to split up by boundary(“word”) than " "?
boundary() is able to handle seperation by punctuation, " " would only seperate by spaces
3. What does splitting with an empty string ("") do? Experiment, and then read the documentation.
Splits each charracter
```{r}
str_split(x,"")
```

